### 2024-02-05 README.Rmd
output as table

-   **st_bridges()**

*Create a neighbours list, matrix, or `sf` dataframe containing a neighbours list or matrix as column "nb", while accounting for islands.*

-   **st_quickmap_nb()**

*Check contiguities visually on map.*

-   **st_check_islands()**

*Check assignment of island contiguities in a dataframe.*

-   **st_manual_join_nb()**

-   **st_manual_cut_nb()**

*Make manual changes to any connections.*

@@

-   **st_augment()**

*Augment the original dataframe with model predictions.*

-   **st_quickmap_preds()**

*Generate quick maps of these predictions.*

>>>>

| function:               | purpose:                                                                                                                                   |
|------------|-----------------------------------------------|
| **st_bridges()**        | *Create a neighbours list, matrix, or `sf` dataframe containing a neighbours list or matrix as column "nb", while accounting for islands.* |
| **st_quickmap_nb()**    | *Check contiguities visually on map.*                                                                                                      |
| **st_check_islands()**  | *Check assignment of island contiguities in a dataframe.*                                                                                  |
| **st_manual_join_nb()** | *Make manual changes to any connections.*                                                                                                  |
| **st_manual_cut_nb()**  | *Make manual changes to any connections.*                                                                                                  |

@@

| function:               | purpose:                                                 |
|-----------------|-------------------------------------------------------|
| **st_augment()**        | *Augment the original dataframe with model predictions.* |
| **st_quickmap_preds()** | *Generate quick maps of these predictions.*              |
